Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-17 ba_resubmit/kundinger_resubmit2.tex
formatted appendix in A,B,C, etc fashion.

	\section{Appendix}
	\label{sec:appendix}

	\hypertarget{bayes-estimate}{%
		\subsection{Bayes Estimate}
		\label{bayes-estimate}}

@@

	\hypertarget{app:derivations}{%
	\subsection{Derivations of Full Conditionals}\label{app:derivations}}

@@

	\hypertarget{partial}{%
	\subsection{Accuracy under Partial Estimates}\label{partial}}

@@

	\hypertarget{appendix-sim}{%
		\subsection{Traceplots for Simulation Study}\label{app:appendix-sim}}
	Figures \ref{fig:sim_overlap_trace}, \ref{fig:sim_m_trace}, and \ref{fig:sim_u_trace} are traceplots for one of the 900 linkage tasks that comprise the simulation in Section \ref{accuracy}. It is set up with one error across the linkage fields and 50 duplicates across files. Traceplots across other settings exhibit similar behavior. Note that traceplots for $\bm{u}$ parameters show very little variation because the overwhelming majority of record pairs are nonmatching.

@@

	\hypertarget{appendix-speed}{%
	\subsection{Additional Speed Simulation Study}\label{app:appendix-speed}}
	Figures \ref{fig:app-speed1} and \ref{fig:app-speed2} illustrate that different constructions of the comparison vectors lead to similar speed gains. We replicate the speed study of Section \ref{speed} under different settings. Here, we use four fields of comparison, each with three possible levels of agreement, resulting in $3^4 = 81$ possible patterns. The $\bm{m}$ and $\bm{u}$ parameters for this simulation are shown Table \ref{Tab:distributions_2}.

@@

	\hypertarget{appendix-es}{%
		\subsection{Traceplots for El Salvador Case Study}\label{app:appendix-es}}

>>>>

%	\section{Appendix}
%	\label{sec:appendix}

\appendix

	\hypertarget{bayes-estimate}{%
		\section{Bayes Estimate}
		\label{bayes-estimate}}

@@

	\hypertarget{app:derivations}{%
	\section{Derivations of Full Conditionals}\label{app:derivations}}

@@

	\hypertarget{partial}{%
	\section{Accuracy under Partial Estimates}\label{partial}}

@@

	\hypertarget{appendix-sim}{%
		\section{Traceplots for Simulation Study}\label{app:appendix-sim}}
	Figures \ref{fig:sim_overlap_trace}, \ref{fig:sim_m_trace}, and \ref{fig:sim_u_trace} are traceplots for one of the 900 linkage tasks that comprise the simulation in Section \ref{accuracy}. It is set up with one error across the linkage fields and 50 duplicates across files. Traceplots across other settings exhibit similar behavior. Note that traceplots for $\bm{u}$ parameters show very little variation because the overwhelming majority of record pairs are nonmatching.

@@

	\hypertarget{appendix-speed}{%
	\section{Additional Speed Simulation Study}\label{app:appendix-speed}}
	Figures \ref{fig:app-speed1} and \ref{fig:app-speed2} illustrate that different constructions of the comparison vectors lead to similar speed gains. We replicate the speed study of Section \ref{speed} under different settings. Here, we use four fields of comparison, each with three possible levels of agreement, resulting in $3^4 = 81$ possible patterns. The $\bm{m}$ and $\bm{u}$ parameters for this simulation are shown Table \ref{Tab:distributions_2}.

@@

	\hypertarget{appendix-es}{%
		\section{Traceplots for El Salvador Case Study}\label{app:appendix-es}}
